Figure 2 and figure 2 supplementary material

### 2023-07-24 Figures/Figure2.Rmd
minor fix dplyr Figure2.Rmd

formatted_cors <- function(df, cor.stat){
  cors(df, cor.stat) %>%
    map(~rownames_to_column(.x, var="measure1")) %>%
    map(~pivot_longer(.x, -measure1, "measure2")) %>%
    bind_rows(.id = "id") %>%
    pivot_wider(names_from = id, values_from = value) %>%
    dplyr::rename(p = P) %>%
    mutate(sig_p = ifelse(p < .05, T, F),
           p_if_sig = ifelse(sig_p, p, NA),
           r_if_sig = ifelse(sig_p, r, NA)) 
}
################################################################################

>>>>

formatted_cors <- function(df, cor.stat){
  cors(df, cor.stat) %>%
    map(~rownames_to_column(.x, var="measure1")) %>%
    map(~pivot_longer(.x, -measure1, names_to = "measure2")) %>%
    bind_rows(.id = "id") %>%
    pivot_wider(names_from = id, values_from = value) %>%
    dplyr::rename(p = P) %>%
    mutate(sig_p = ifelse(p < .05, T, F),
           p_if_sig = ifelse(sig_p, p, NA),
           r_if_sig = ifelse(sig_p, r, NA)) 
}
################################################################################
